---
title: "Survey"
hide-description: false
description: ""
execute:
  warning: false
---

## Eurobarometer

## How to access data

EUI members can access Eurobarometer data via GESIS (the German social science infrastructure service provider) and via ICPSR (the Inter-University Consortium for Political and Social Research archive).


### Eurobarometer via GESIS

Access to primary Eurobarometer data is provided by the GESIS Eurobarometer Data Service:

- Standard and Special Eurobarometer
- Mannheim Eurobarometer Trend File
- Central and Eastern Eurobarometer
- Candidate Countries Eurobarometer
- Flash Eurobarometer surveys.

### Eurobarometer via ICPSR

EUI members also have access to Eurobarometer files hosted by the ICPSR data archive. Data from ICPSR can only be downloaded by Library administrator. Follow these instructions:

- Locate the required data study number(s) in the ICPSR data catalogue
- Send the study number of the dataset required to econlibrary@eui.eu
- Indicate the format in which the data are required (Stata, SAS &c.)
- The Library provides access via MS OneDrive.
- ICPSR instructions on using ZIP files to compress and decompress data are on this page

EUI ICT Service instructions on using ZIP files to compress and decompress data are on this page

[Read the Responsible Use Statement on the ICPSR site](https://www.icpsr.umich.edu/web/pages/datamanagement/lifecycle/access.html).

European statistical data resources (EUI Library).

 
## GESIS survey Data


Data was taken from [here](https://search.gesis.org/?source=%7B%22sort%22%3A%5B%7B%22date_recency%22%3A%7B%22order%22%3A%22desc%22%7D%7D%5D%2C%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%5B%7B%22query_string%22%3A%7B%22query%22%3A%22economic%22%2C%22default_operator%22%3A%22AND%22%7D%7D%5D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22EB%20-%20Standard%20and%20Special%20Eurobarometer%22%7D%7D%5D%7D%7D%7D&lang=en) with data format ".sav"

Date(s) of Data Collection: 12.01.2023 - 06.02.2023

GESIS, Cologne. ZA7953 Data file Version 1.0.0, https://doi.org/10.4232/1.14081
Other Title (type): Standard Eurobarometer 98 (COVID-19 Pandemic) (Subtitle)

Abstract:
Since the early 1970s the European Commission´s Standard & Special Eurobarometer are regularly monitoring the public opinion in the European Union member countries. Principal investigators are the Directorate-General Communication and on occasion other departments of the European Commission or the European Parliament. Over time, candidate and accession countries were included in the Standard Eurobarometer Series. Selected questions or modules may not have been surveyed in each sample. Please consult the basic questionnaire for more information on country filter instructions or other questionnaire routing filters. In this study all question modules are in the standard Eurobarometer context: 1. Standard EU and trend questions, 2. Europeans’ priorities, 3. The EU and the Coronavirus pandemic, 4. European citizenship, 5. The EU’s response to the war in Ukraine, 6. Media use and political information.

```{r}

library(retroharmonize)
tmp <- tempfile(fileext = ".sav")
haven::write_sav(mtcars, tmp)
haven::read_sav(tmp)

```


## Excel data from EU commission 

For data taken from EU with ".xslx" format taken from [here](https://data.europa.eu/data/datasets/s2970_fl531_eng?locale=en) and it's only for testing purpose.



```{r}

library(readxl)
library(tibble)
library(dplyr)

# Specify the path to your Excel file
excel_file <- "survey/fl_531_volume_C_SK.xlsx" 

# Get the names of all sheets in the Excel file
sheet_names <- excel_sheets(excel_file)

# Initialize an empty tibble to store the combined data
combined_data <- tibble()

# Read each sheet (starting from the third sheet) and append to the combined data frame
for (sheet_name in sheet_names[3:length(sheet_names)]) {
  # Define the range to read (rows 11 to 26)
  range_to_read <- cell_rows(11:58)

  # Read the current sheet as a tibble within the specified range
  current_data <- as_tibble(
    read_excel(excel_file, sheet = sheet_name, range = range_to_read)
  )

  # Add a column to identify the sheet (survey question)
  current_data$SheetName <- sheet_name

  # Bind the current data to the combined data frame
  combined_data <- bind_rows(combined_data, current_data)
}
combined_data <- na.omit(combined_data)

# # Define a threshold for NA proportion
# threshold <- 0.9 # Example: 90% NA values
# 
# # Remove columns where the majority of values are NA
# na_cols <- sapply(combined_data, function(x) mean(is.na(x))) > threshold
# combined_data <- combined_data[, !na_cols]
# 
# # Display the structure of the combined data frame
str(combined_data)

# Optionally, view the first few rows of the combined data
knitr::kable(head(combined_data))


```

